Background for transient faults in asynchronous circuits

### 2019-11-24 draft_final.tex
Lemma 3 1st change

Next we show that if a single transient fault occurs on any wire, the fault free half circuit will be equivalent to the original circuit in some sense.  
Suppose a fault happens in the B-half, according to Lemma 1, the A-half can never be in a state inconsistent to the original circuit.  But we have not proved that the A-half does not stop prematurely compared to the original circuit.  Towards this goal, we prove two lemmas:  Lemma 3 shows if a single fault occurs on the $c2$ or $c3$ wires of some wire $w$, the output wires still follow the original state graph.  Lemma 4 shows if a fault occurs on any of the other wires, then the $c2$ or $c3$ wires follow a similar state graph as the non-fault case and thus the output wire pairs can never be different at deadlock.  Then these lemmas combine to show that there is no deadlock.
A complete trace is defined similarly for the fault-tolerant circuit.  That is, the trace after mapping must be a complete trace in the original circuit.  The completeness property must be treated separately because there are two halfs in the fault-tolerant circuit and one side needs the other to transition.  Thus, we need to show that even in the presence of a transient fault, each wireblock will eventually transition.

@@

\begin{lemma}[3]
For any trace $\sigma$ in the fault-tolerant circuit, if a single transient fault occurs on wires $c2^B$ or $c3^B$ of some wire block $w$ at any point in the trace, then $h^{B}(\sigma_n)$ is a prefix of a trace in the original circuit for all $n \in \mathbb{N}$.
\end{lemma}
%need major rewording maybe after defining faulty trace
\begin{figure}
  \centering
    \includegraphics{L3helperfull}
  \caption{The projection of the states in figure \ref{fig:l21} from Lemma 2.1 onto the wires $c1^A$, $c1^B$ and $w^A$, $w^B$.  This forms the input and output characteristic of a wire block under normal operation.}
  \label{fig:l3helper}
\end{figure}

@@

\begin{lemma}[4]
For every trace $\sigma$ in the fault-tolerant circuit, if a fault occurs in the B-half on a wire other than $c2^B$ or $c3^B$, the following property is true: the $c2$ and $c3$ wires of each wire block of the circuit follow the state graph of Figure \ref{fig:l4}.
\end{lemma}
\begin{proof}
The fault is in the B-half while the A-half is fault-free so Lemma 1 applies for the A-half.  We will show by induction on $n$ that Lemma 4 is true for each prefix of the trace, $\sigma_n$.  %how to make it seem like prefix not trace modifies sigma_n
We only analyze cases 1-5 because transitions from case 6 onwards is symmetric to transitions from case 1 onwards with 0's and 1's inverted, until the state eventually loops back to case 1.  For example, case 6 is symmetric to case 1 and has the corresponding transition to case 7, which is symmetric to case 2 with corresponding transitions and so on.\\

>>>>

The next major theorem states that a faulty trace in the fault-tolerant circuit maps to a fair trace in the original circuit.  To prove this, we need to show that if a wireblock in the fault-tolerant circuit is excited, it will eventually transition.  We assume the fault happens only in the B-half and in some wireblock $v$.  By semi-modularity, the excited A-half of the wireblock remains excited until its output transitions.  The transition is guaranteed to happen only if the B-half logic block is permanently excited too, and to the same value as the A-half.\\

We first take note of some properites of semi-modular and fault-tolerant circuits.  \\

Lemma 3.2 from Beerel \& Meng states that all cycles of states in live semi-modular circuits must contain all signal transitions.\\

Thus, if the theorem that we want to prove is false, then there exists some excited wireblock that does not transition.  B\&M's lemma implies that after the mapping, the original circuit stops in some state.  This also implies that the A-half of the fault-tolerant circuit also stops.  Assuming the A-half stops, we prove that the output pairs eventually have the same value, that is, $w^A=w^B$ for each wireblock $w$.  This is split into two cases, when the fault occurs on the $c2^B$ or $c3^B$ wires of $v$, and when the fault occurs on the remaining wires $c1^B$ or $v^B$.  
%Lemma 3 shows that if the A-half stops and the single fault occurs on the $c2^B$ or $c3^B$ wires of $v$, .

%Next we show that if a single transient fault occurs on any wire, the fault free half circuit will be equivalent to the original circuit in some sense.  Suppose a fault happens in the B-half, according to Lemma 1, the A-half can never be in a state inconsistent to the original circuit.  But we have not proved that the A-half does not stop prematurely compared to the original circuit.  Towards this goal, we prove two lemmas:  Lemma 3 shows if a single fault occurs on the $c2$ or $c3$ wires of some wire $w$, the output wires still follow the original state graph.  Lemma 4 shows if a fault occurs on any of the other wires, then the $c2$ or $c3$ wires follow a similar state graph as the non-fault case and thus the output wire pairs can never be different at deadlock.  Then these lemmas combine to show that there is no deadlock.  A complete trace is defined similarly for the fault-tolerant circuit.  That is, the trace after mapping must be a complete trace in the original circuit.  The completeness property must be treated separately because there are two halfs in the fault-tolerant circuit and one side needs the other to transition.  Thus, we need to show that even in the presence of a transient fault, each wireblock will eventually transition.

@@

\begin{lemma}[3]
For any faulty trace $\sigma$ in the fault-tolerant circuit where the A-half stops, if the transient fault occurs on wires $c2^B$ or $c3^B$ of some wire block $v$, then the circuit stops and for each wireblock $w$, wire values $w^A=w^B$.
\end{lemma}
%need major rewording maybe after defining faulty trace
\begin{figure}
  \centering
    \includegraphics{L3helperfull}
  \caption{The projection of the states in figure \ref{fig:l21} from Lemma 2.1 onto the wires $c1^A$, $c1^B$ and $w^A$, $w^B$.  This forms the input and output characteristic of a wire block under normal operation.}
  \label{fig:l3helper}
\end{figure}

@@

\begin{lemma}[4]
For any faulty trace $\sigma$ in the fault-tolerant circuit where the A-half stops, if the transient fault occurs on wires $c1^B$ or $v^B$ of some wireblock $v$, then the circuit stops and for each wireblock $w$, wire values $w^A=w^B$.
\end{lemma}

\begin{proof}
The fault is in the B-half while the A-half is fault-free so Lemma 1 applies for the A-half.  We will show by induction on $n$ that Lemma 4 is true for each prefix of the trace, $\sigma_n$.  %how to make it seem like prefix not trace modifies sigma_n
We only analyze cases 1-5 because transitions from case 6 onwards is symmetric to transitions from case 1 onwards with 0's and 1's inverted, until the state eventually loops back to case 1.  For example, case 6 is symmetric to case 1 and has the corresponding transition to case 7, which is symmetric to case 2 with corresponding transitions and so on.\\
